Paper 2: Vitamin D

### 2018-04-10 doc/vitaminD.Rmd
subgroup analysis with only kidney dysfunction subjects
determine n of subjects under assay detection limit

# for sensitivity analysis
m <- ds %>% 
  dplyr::filter(fVN != "6Year")

@@

dsBase %>% 
  scatter_plot_slides("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D (nmol/L)",
               "log uVDBP:cr (μg/mmol)")

>>>>

# for sensitivity analysis
m <- ds %>% 
  # dplyr::mutate(followUp = )
  dplyr::filter(fVN != "6Year")

@@

dsBase %>% 
  # dplyr::filter(acrStatus != "Normoalbuminuria") %>% 
  scatter_plot_slides("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D (nmol/L)",
               "log uVDBP:cr (μg/mmol)")
